---
title: 'Reproducible Research: Peer Assessment 1'
output:
  pdf_document: default
  html_document:
    keep_md: yes
  word_document: default
---

```{r}
setwd("F:/-RdC-/Coursera/Coursera-DataScience/5、Reproducible Research/Assignment/A1")

library(knitr)
library(dplyr)
library(lubridate)
library(ggplot2)

## Loading and preprocessing the data
Activity<-read.csv("./data/activity.csv",header=T,na.strings="NA")

Activity$date_time<- 
  ymd_hms(paste(Activity$date," " 
                ,substr(sprintf("%04.0f", Activity$interval),1,2)
                 ,":",substr(sprintf("%04.0f", Activity$interval),3,4),":00",sep=""))

## What is mean total number of steps taken per day?
PerDateSum<-Activity %>%
  group_by(date) %>%
  summarise(sum=sum(steps,na.rm=T))

hist(PerDateSum$sum,main="The Total Number Of Steps Taken Each Day"
     ,xlab="Total Steps")
```

The mean total number of steps taken per day equal `r mean(PerDateSum$sum)`

The median total number of steps taken per day equal `r median(PerDateSum$sum)`




```{r}
## What is the average daily activity pattern?
IntervalAvg<-Activity %>%
  group_by(interval) %>%
  summarise(avg=mean(steps,na.rm=T))

plot(IntervalAvg,type="l",main="The Average Number of  Steps Taken")
```

The  `r IntervalAvg[which.max(IntervalAvg$avg),]$interval` 5-minute interval  ,on average across all the days in the dataset ,contains the maximum number of steps.

```{r}
## Imputing missing values
FilledData<-Activity

for (i in unique(FilledData$interval))
{
  FilledData[(is.na(FilledData$steps) 
              & FilledData$interval==i),1]<-IntervalAvg[ which(IntervalAvg$interval==i),2]
}

FilledPerDateSum<-FilledData %>%
  group_by(date) %>%
  summarise(sum=sum(steps,na.rm=T))

hist(FilledPerDateSum$sum,main="The Total Number Of Steps Taken Each Day(filled)"
     ,xlab="Total Steps")
```


The mean total number of steps taken per day from the dataset which filled in all of the missing values  equal `r mean(FilledPerDateSum$sum)` 

The median total number of steps taken per day from the dataset which filled in all of the missing values  equal `r median(FilledPerDateSum$sum)` 

These values differ from the estimates from the first part of the assignment .

```{r}
## Are there differences in activity patterns between weekdays and weekends?

i<-1
weekends<-""
while (i<nrow(FilledData)+1){
if(weekdays(FilledData$date_time[i]) %in% c("星期六","星期日"))
  {weekends[i]<-"weekends"}
else { weekends[i]<-"weekdays"}
i<-i+1
}

FilledData$WK<-weekends

FilledWkAvg<-  FilledData %>%
  group_by(WK,interval) %>%
  summarise(avg=mean(steps,na.rm=T)) %>%
  as.data.frame()

ggplot(FilledWkAvg,aes(x=interval,y=avg,group=WK))+geom_line()+facet_wrap(~WK,nrow=2)

```


